Figures

### 2020-04-15 manuscript/figures.Rmd
explain panel discrepancies

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) nearshore slope versus inlake slope. Also shown is a 1:1 line for comparison.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```

```{r depth_model_metrics, fig.cap = "Model fit and predictive accuracy metrics for all combinations of true (inlake slope, deepest point distance) and proxy (nearshore slope, visual center distance) metrics. Tiles are colored by their $R^2$ values and labeled with their RMSE values.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/depth_model_metrics-1.pdf")
```

@@

```{r depth_model_grid_resid, fig.cap = "Depth model residuals by shape and reservoir class.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/02_depth_model_grid_resid-1.pdf")
```

>>>>

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) nearshore slope versus inlake slope. A dashed 1:1 line is shown for comparison. Cross-section shape and reservoir class plots are not identical because not all lakes had a reservoir classification exceeding a 0.75 probability confidence level.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```

```{r depth_model_metrics, fig.cap = "Model fit and predictive accuracy metrics for all combinations of true (inlake slope, deepest point distance) and proxy (nearshore slope, visual center distance) metrics. Tiles are colored by their $R^2$ values and labeled with their RMSE values.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
# see 02_depth_model.Rmd
knitr::include_graphics("../figures/depth_model_metrics-1.pdf")
```

@@

```{r depth_model_grid_resid, fig.cap = "Depth model residuals by cross-section shape and reservoir class.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
# see 02_depth_model.Rmd
knitr::include_graphics("../figures/02_depth_model_grid_resid-1.pdf")
```
